SSRP Report based on *Energy Saving May Kill: Evidence from the Fukushima Nuclear Accident* by He and Tanaka (2019)

### 2024-02-15 other/ssrp/ssrp_report.qmd
Modified ssrp

---
title: "SSRP Report based on *Energy Saving May Kill: Evidence from the Fukushima Nuclear Accident* by He and Tanaka (2019)"
author:
  - Yi Fei Pang
  - Irene Huynh
  - Tara Chakkithara
thanks: "Code and data are available at: https://github.com/apang00/Energy-Policy.git"
date: today
date-format: long
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "SSRP Report based on *Energy Saving May Kill: Evidence from the Fukushima Nuclear Accident* by He and Tanaka (2019)"
author:
  - Yi Fei Pang
  - Irene Huynh
  - Tara Chakkithara
thanks: "Code and data are available at: https://github.com/apang00/Energy-Policy.git"
date: today
date-format: long
format: pdf
bibliography: references.bib
---
